Offshore Modeling - Manuscript Model

### 2020-03-06 2019_edits/R/offshore_analyses/final_analyses/Manuscript_Offshore_Modeling.Rmd
put manuscript figures in folder

year_plot + year_foa

@@

rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
rs_plot_full + rs_plot_4
```

@@

@@

ggplot() +
  geom_sf(data = szones, fill = NA) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  labs(x = NULL, y = NULL)  +
  scale_y_continuous(breaks = c(25,30)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))
```

>>>>

figure_4 <- year_plot + year_foa

figure_4

ggsave(figure_4, 
       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure4.tiff"), 
       height = 4, 
       device = "tiff")
```

@@

rs_plot_full <- rs_plot_3 + theme(legend.position = "none")
figure_3 <- rs_plot_full + rs_plot_4

figure_3

ggsave(figure_3, 
       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure3.tiff"), 
       height = 4, 
       device = "tiff")
```

@@

#Savie it
ggsave(p, 
       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure5.tiff"), 
       device = "tiff")

@@

sz_plot <- ggplot() +
  geom_sf(data = szones, fill = NA) +
  geom_sf(data = usmap) +
  geom_sf(data = mex) +
  geom_text(data = sz_df, aes(long, lat, label = SZ), size = 3.5) +
  coord_sf(xlim = c(-98, -81), ylim = c(24, 31)) +
  labs(x = NULL, y = NULL)  +
  scale_y_continuous(breaks = c(25,30)) +
  annotation_north_arrow(
    height = unit(0.4, "in"),
    location = "bl", 
    which_north = "true", 
    pad_x = unit(0, "in"), 
    pad_y = unit(0, "in"),
    style = north_arrow_fancy_orienteering) +
  annotation_scale(
    pad_x = unit(0.5, "in"))

sz_plot

# Export
ggsave(sz_plot, 
       filename = here::here("2019_edits/R/offshore_analyses/final_analyses/manuscript_figs", "Figure1.tiff"), 
       height = 4, 
       device = "tiff")
```
